%%%%%% Stuff to add:
% invited (declined) seminars
% extending knowledge: reporters, master gardner, etc.


\documentclass[letterpaper,10pt]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{etaremune}
%\usepackage{eurofont}
\usepackage{verbatim}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
%\usepackage{setspace}
% Set your name here
\def\name{Prashant Anantharaman}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{https://prashant.at}

%Add in-line comments
\newcommand{\ignore}[1]{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {population genetics, maize, plant evolution},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
%\ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

%ADDRESS
\begin{minipage}{0.55\linewidth}
    \href{}{Master's Candidate,}\\
  \href{}{Department of Computer Science,}\\
  \href{}{Dartmouth College, NH, USA.}\\
\end{minipage}
\begin{minipage}{0.35\linewidth}
  \begin{tabular}{ll}
    Phone: & (510) 904-8439 \\
    Email: & \href{mailto:lists@prashant}{lists@prashant.at} \\
    Web: & \href{https://prashant.at}{https://prashant.at}, \href{http://www.twitter.com/prashantbarca/}{@prashantbarca} \\
  \end{tabular}
\end{minipage}

%EDUCATION
\section*{Education}
\begin{itemize}
\setlength\itemsep{0.5ex}
\item \textit{Master of Science} in Computer Science -- August 2015 -- June 2017\\\textbf{Dartmouth College}, NH, USA.\\
    \textit{Research Area}: Systems Security\\
    \textit{Advisors}: Dr. Sean W. Smith and Dr. Sergey Bratus
\item \textit{Bachelor of Engineering} in Computer Science and Engineering -- August 2011 -- May 2015.\\ \textbf{College of Engineering Guindy}, Chennai, India\\
    \textit{Research Area}: Compilers and Systems\\
    \textit{Thesis}: Code Compaction in LLVM IR.\\
    \textbf{TCS Best Senior Thesis Award.}\\
    \textit{Thesis Advisor}: Dr. Arul Siromoney
\end{itemize}

\section*{Experience}
\begin{itemize}
\setlength\itemsep{0ex}
\item \textbf{SRI International, Menlo Park, CA, USA} -- Internet-of-Things Security and Privacy Center\\
    \textit{Student Associate.} Advisors: Dr. Michael Locasto, Dr. Gabriela Ciocarlie, Dr. Ulf Lindqvist.\\
    Worked on an independent project to build \textit{Language-theoretic security} compliant clients for application layer Internet-of-Things protocols. 
\item \textbf{Samsung R\&D Institute, Bangalore, India} -- Intelligent Search Team\\
    \textit{Student Trainee.} Advisor: Mohan Sundar B.\\
    Worked on an independent project of designing a graph searching system using Neo4J and Apache Giraph.
\end{itemize}


%\begin{comment}
%INSTRUCTION & Advising
%PUBS
\section*{Publications}


%SUBMITTED
\subsection*{Preprints}
\begin{itemize}
    \item {\bf P. Anantharaman}, M. Locasto, G. Ciocarlie, U. Lindqvist.\\
        "Building hardened Internet-of-Things implementations using Language-theoretic Security"\\
        IEEE Symposium on Security and Privacy -- Language-theoretic Security Workshop.\\
        May 2017 (Submitted)
\end{itemize}

%PRINT/PRESS
\subsection*{Conferences and Workshops} %don't edit below line on H-index, use script instead

\begin{etaremune}
\setlength\itemsep{0ex}
\item {\bf P. Anantharaman}, K. Palani, D. Nicol, S.W. Smith.\\
    "I am Joe's Fridge: Scalable Identity in the Internet of Things"\\
    IEEE International Conference on Internet of Things.\\
    December 2016.
\item G. Ramakrishnan, {\bf P. Anantharaman}, and S. Mukherjee.\\
    "Proactive Resource Provisioning Model for Cloud Federation."\\
    International Conference on Distributed Computing and Internet Technology. Springer International Publishing,\\
    January 2016.
\end{etaremune}

\subsection*{Posters}

\begin{etaremune}
\setlength\itemsep{0ex}
\item \textbf{P. Anantharaman}, J. P. Brady, S. Bratus, I. R. Jenkins, M. Millian, D.M. Nicol, K. Palani, E. Reed, S.W. Smith\\
    "Increasing Cyber-Resilience of Large-Scale and Long-Lived Energy Delivery Infrastructure (EDI)"\\
    2nd CREDC Industry Workshop ,Tempe, AZ\\
    March 2017


\item \textbf{P. Anantharaman}, D.M. Nicol, K. Palani, E. Reed, S. W. Smith\\
    "Scalable Identity in the Smart Grid"\\
    2nd CREDC Industry Workshop ,Tempe, AZ\\
    March 2017
\item  K. Palaki, {\bf P. Anantharaman}, D.M. Nicol, S. W. Smith\\
    "Namespace and Cryptographic Complexities in the Smart Grid"\\
    1st CREDC Industry Workshop ,Champaign, IL\\
    March 2016
\end{etaremune}

\section*{Teaching Experience}
\begin{itemize}
\setlength\itemsep{0ex}
\item Teaching Assistant for \textit{Programming Languages (COSC 59)}, September 2016-- November 2016.
		\subitem Fall 2016 (1 lecture). Instructor -- Dr. Sergey Bratus.
\item \textit{Ruby on Rails} Instructor at FSFTN Summer Camp, June 2015.
    \subitem Number of Participants: 120.
    \subitem Venue: IIT Madras.
\end{itemize}


%SEMINARS
\section*{Talks and Presentations}
\begin{itemize}
\setlength\itemsep{0ex}
\item \textit{Building vertically hardened Industrial-Control-Systems applications using Language-theoretic security}\\ 2nd CREDC Industrial Workshop\\ Tempe, AZ\\ March 28th 2017.
\item \textit{Scalability Identity in the Internet of Things}\\ IEEE International Conference on Internet of Things\\ Chengdu, China\\ December 18th 2016.
\end{itemize}

%AWARDS
\section*{Selected Fellowships and Awards}
\setlength\itemsep{0ex}
\begin {itemize}
\setlength\itemsep{0ex}
\item 50\% fee scholarship for first year of masters at Dartmouth College. 
\item TCS Award for Best Senior Thesis -- 2015
\end{itemize}

\end{document}
