%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Prashant Anantharaman 
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Prashant Anantharaman}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    New No. 11, Patel Street                            \hfill Home: +91 44 43565924          \vspace{0mm}\\\vspace{0mm}%
    Kodambakkam, Near Railway Station                          \hfill Mobile: +91 9791190892          \vspace{0mm}\\\vspace{0mm}%
    Chennai, Tamil Nadu, India-600024      
    \hfill E-mail: prashant.barca@gmail.com, \vspace{0mm}\\\vspace{-4.5mm}%
    \hfill prashant.@prashant.at \vspace{0mm}\\\vspace{-4.5mm}%

	\section{\mysidestyle Personal\\Information}

Date of Birth: 11th October,1993      \hfill Age: 21 years \vspace{0mm}\\\vspace{0mm}%
Languages Known: Tamil, English, Hindi, Marathi(Basic) \vspace{0mm}\\\vspace
{0mm}% 
    %__________________________________________________________________________________________________________________
    % Interests
    \section{\mysidestyle Vision}

Engage in lifelong learning, so as to remain up to date with the current trends in the profession and be one of the leaders in the technological society. 
    %__________________________________________________________________________________________________________________
    % Education
    \\\\\section{\mysidestyle Education}

    \textbf{College of Engineering Guindy, Anna University}, Sardar Patel Road, Chennai-25 \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.E in Computer Science and Engineering with a current CGPA of 8.30(After 6 semesters)} \hfill \textbf{June 2011 -- present}\vspace{-3mm}\vspace{-1mm}%
        \item Expected graduation date: June 2015
    
    \textbf{Chettinad Vidyashram}, R.A Puram, Chennai-26 \vspace{2mm}\\\vspace{1mm}%
    \textsl{Class 12, CBSE 89.4 percentage} \hfill \textbf{March 2011}\vspace{-3mm}\vspace{-1mm}%

    \textbf{Smt. Sulochanadevi Singhania School}, Thane, Maharashtra-400607 \vspace{2mm}\\\vspace{1mm}%
    \textsl{Class 10, ICSE 91.8 percentage} \hfill \textbf{March 2009}\vspace{-3mm}\\\vspace{-1mm}%
%__________________________________________________________________________________________________________________
    % Education 
    \\\\\section{\mysidestyle Related\\Courses} 
    \textbf{CISCO Certified Network Associate(CCNA)} \\Pursuing the CCNA Academic Certification Programme at the CISCO Labs, Anna University. Completed phases I, II and III and IV is in progress. \vspace{2mm}\\\vspace{1mm}%
    \textbf{Attended a 5 day workshop on Free Softwares by Free Software Movement Karnataka(FSMK)}\\The five day workshop included the introduction to several free and open source softwares. Held from 18th to 22nd January, 2013.  \vspace{2mm}\vspace{1mm}%
    \\\textbf{Organized a 5 day workshop on Free Software Technologies for Free Software Foundation Tamil Nadu(FSFTN) at IIT, Madras}\\Conducted from 18-22nd June, 2013. Included Free softwares like Drupal, Ruby on Rails, OpenStack,Python, etc  \vspace{2mm}\vspace{1mm}%

    %__________________________________________________________________________________________________________________
    % Technical Experiences
    \\\\\section{\mysidestyle Experience}

   
    \\\textbf{Internship at Samsung R\&D Institute, Bangalore} \\ Worked on Graph Database based systems using Apache Giraph and Neo4J.\\
\textsl{15th May,2014 to 11th July, 2014 }\\
  \\  Software(s) used -  \textsl{Apache Giraph, Neo4J, Ruby on Rails}\\
    \\\textbf{Intern at Dangote Industries, Lagos, Nigeria} \\Worked on the integration of hardware equipment with their ERP solution.\\
\textsl{29th November,2013 to 15th December, 2013 }\\
\\    Software(s) used -  \textsl{Dot net, C#}\\
    \\\textbf{Final Year Project - LLVM IR} \\Working on Code Compaction in LLVM IR Compiler Infrastructure. \vspace{2mm}\\\vspace{1mm}%
    Software(s) used -  \textsl{C,C++}\\
    \\\textbf{Tamil OCR and Error Correction} \\Working on a project being funded by "Centre for Technology Development and Transfer, Anna University" \vspace{2mm}\\\vspace{1mm}%
    Software(s) used -  \textsl{Ruby on Rails, Java}\\
    \\\textbf{Khelo, A sports programming language} \\Developed an interpreter based language as a "Design of Compilers" project. \vspace{2mm}\\\vspace{1mm}%
    Software(s) used -  \textsl{Ruby(Lex and Yacc)}\\
    \\\textbf{File Sharing Portal} \\Developed a "Social Network for sharing of Files and Videos". The source code to which can be found on https://github.com/ProjectAlex/laughing-adventure . \vspace{2mm}\\\vspace{1mm}%
    Software(s) used -  \textsl{Ruby on Rails}\\
    \\\textbf{Database Managament Systems Project} \\Designed and implemented a time table management system for the Computer Science and Engineering Department \vspace{2mm}\\\vspace{1mm}%
    Software(s) used -  \textsl{mysql,monodevelop,phpmyadmin}\\
    \\\textbf{Developed CEG's GNU/Linux Users Group Website}\\Hosted at http://ceglug.github.io and the code can be found at https://github.com/ceglug/ceglug.github.io
    \\Software(s) used -  \textsl{Jekyll, HTML, CSS, Javascript}\\
    \\\textbf{Developed an Ubuntu Based Distribution called "CEGLUG Distro"} \\For the CEG GNU/Linux Users Group (CEGLUG) \vspace{2mm}\\\vspace{1mm}%
    Software(s) used -  \textsl{remastersys}\\
    \\\textbf{Created my own website site} \\Designed and hosted at http://prashant.at \vspace{2mm}\\\vspace{1mm}%
    Software(s) used -  \textsl{HTML, CSS, Javascript}\\
    
    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming\\Skills}\\ 
    \textbf{Proficient in -}  Ruby, C, C++, Shell scripting, Python, JAVA, DOT NET, C#
\\\textbf{Basic knowledge of -}  \LaTeXe

    \section{\mysidestyle Other Software\\Skills} \\
    \textbf{Tools I Use}  \\Vim Text Editor, Ruby on Rails, Git version control(this resume itself is hosted at \\https://github.com/prashantbarca/resume ), phpmyadmin, Dia, ArgoUML, Umbrello
    \\\textbf{Databases} - \\Mysql, MariaDB, Postgresql, SQLite, ORACLE SQL
    \\\textbf{GitHub Account -}  https://github.com/prashantbarca
    \\\textbf{Codecademy Account -}  http://www.codecademy.com/users/javasolver06191
    \\\section{\mysidestyle Operating systems}\\ 
    \\ GNU/Linux(Debian,CentOS,RHEL,Fedora,ArchLinux,Ubuntu),Windows 7,Windows XP 

    %__________________________________________________________________________________________________________________

	 \\\\\section{\mysidestyle Other\\Accompli-\\shments}\\ 
    \textbf{Worked as Junior Correspondent at "The Guindy Times" -}"The Guindy Times" is the Official Campus Magazine of Anna University,Chennai
    \\\textsl{August 2011-January 2013}
    \\\\\textbf{Working as Executive Member Computer Society Anna University}" CSAU organizes several sessions and events so as to improve the quality of the students at Anna University
    \\\textsl{January 2013 - Present}
\\\\\textbf{An active member of CEGLUG and FSFTN-}CEGLUG is the GNU/Linux Users Group of Anna University,Chennai. We conduct workshops regularly on Python, Ruby, and also other open source softwares like gimp.FSFTN is the Free Software foundation of Tamil Nadu. We work against the restriction of freedom of knowledge to the common man. 
\\\textsl{August 2012 - Present}
    \\\\\textbf{Working as a Student Director of CEG Tech Forum}"CEG Tech Forum" is a student run organization that solely organizes the International Techno-Management Fest "Kurukshetra", under the patronage of UNESCO. I am the leading Web Developer for the CEG Tech Forum, and have developed the websites for the Fest and its corresponding events.
    \\\textsl{April 2014 - Present}

    %__________________________________________________________________________________________________________________

\end{resume}
\end{document}

%____________________________________________________________________________________________________________
% EOF


