%%%%%% Stuff to add:
% invited (declined) seminars
% extending knowledge: reporters, master gardner, etc.


\documentclass[letterpaper,10pt]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{etaremune}
%\usepackage{eurofont}
\usepackage{verbatim}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
%\usepackage{setspace}
% Set your name here
\def\name{Prashant Anantharaman}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{https://prashant.at}

%Add in-line comments
\newcommand{\ignore}[1]{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {population genetics, maize, plant evolution},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
%\ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

%ADDRESS
\begin{minipage}{0.55\linewidth}
    \href{}{Doctor of Philosophy (Ph.D.) Candidate,}\\
  \href{}{Department of Computer Science,}\\
  \href{}{Dartmouth College, NH, USA.}\\
\end{minipage}
\begin{minipage}{0.35\linewidth}
  \begin{tabular}{ll}
    Phone: & (510) 904-8439 \\
    Email: & \href{mailto:lists@prashant}{lists@prashant.at} \\
    Web: & \href{https://prashant.at}{https://prashant.at}, \href{http://www.twitter.com/prashantbarca/}{@prashantbarca} \\
  \end{tabular}
\end{minipage}

%EDUCATION
\section*{Education}
\begin{itemize}
\setlength\itemsep{0.5ex}
\item \textit{Doctor of Philosophy (Ph.D.)} in Computer Science --  June 2017 -- \\\textbf{Dartmouth College}, NH, USA.\\
    \textit{Research Area}: Systems Security\\
    \textit{Advisors}: Dr. Sean W. Smith and Dr. Sergey Bratus
\item \textit{Master of Science} in Computer Science -- August 2015 -- June 2017\\\textbf{Dartmouth College}, NH, USA.\\
    \textit{Research Area}: Systems Security\\
    \textit{Advisors}: Dr. Sean W. Smith and Dr. Sergey Bratus
\item \textit{Bachelor of Engineering} in Computer Science and Engineering -- August 2011 -- May 2015.\\ \textbf{College of Engineering Guindy}, Chennai, India\\
    \textit{Research Area}: Compilers and Systems\\
    \textit{Thesis}: Code Compaction in LLVM IR.\\
    \textbf{TCS Best Senior Thesis Award.}\\
    \textit{Thesis Advisor}: Dr. Arul Siromoney
\end{itemize}

\section*{Experience}
\begin{itemize}
\setlength\itemsep{0ex}
\item \textbf{SRI International, New York, NY, USA} -- Internet-of-Things Security and Privacy Center\\
    June 2018 -- September 2018
    \textit{Student Associate.} \\ Advisors: Dr. Michael Locasto, Dr. Gabriela Ciocarlie, Dr. Ulf Lindqvist.\\
		Device identification and fingerprinting in Internet-of-Things networks using clustering.
\item \textbf{SRI International, Menlo Park, CA, USA} -- Internet-of-Things Security and Privacy Center\\
    June 2017 -- September 2017
    \textit{Student Associate.} \\ Advisors: Dr. Bogdan Copos, Dr. Michael Locasto, Dr. Ulf Lindqvist.\\
    Designing \textit{composite-metrics} for understanding security of Internet-of-Things ecosystems.
\item \textbf{SRI International, Menlo Park, CA, USA} -- Internet-of-Things Security and Privacy Center\\
    June 2016 -- September 2016
    \textit{Student Associate.} \\ Advisors: Dr. Michael Locasto, Dr. Gabriela Ciocarlie, Dr. Ulf Lindqvist.\\
    Building \textit{Language-theoretic security} compliant clients for application layer Internet-of-Things protocols.
\item \textbf{Samsung R\&D Institute, Bangalore, India} -- Intelligent Search Team\\
    May 2013 -- July 2013\\
    \textit{Student Trainee.} \\ Advisor: Mohan Sundar B.\\
    Worked on an independent project of designing a graph searching system using Neo4J and Apache Giraph.
\end{itemize}

\section*{Current Projects}
\begin{itemize}
\setlength\itemsep{0ex}
\item Verified Parser Generators for File Formats
\item IoTHound: Environment-agnostic Device Characterization, Identification, and Monitoring
\item Macaroon-based Key Management Scheme for Publish-subscribe Systems
\end{itemize}

%SEMINARS
\section*{Talks and Presentations}
\begin{itemize}
\setlength\itemsep{0ex}
\item \textit{PhasorSec: Protocol Security Filters for Wide Area Measurement Systems} \\ IEEE International Conference on Communications, Control, and Computing Technologies for Smart Grids \\ Aalborg, Denmark \\ October 29th, 2018
\item \textit{Ghostbusters: A tale of ELF, ABI and Spectre} \\ BSidesAugusta\\ Augusta, GA \\ September 20th, 2018
\item \textit{Going Dark: A Retrospective on the Blackout of 2038} \\ New Security Paradigms Workshop \\ Windsor, UK \\ August 28th, 2018
\item \textit{LangSec for Critical Infrastructure: SSP21, a secure lightweight SCADA protocol} \\ 5th LangSec Workshop at IEEE Symposium on Security and Privacy (Oakland)\\ San Francisco, CA\\ May 24th, 2018
\item \textit{Input Handling Done Right: Building Hardened Parsers using Language-theoretic Security} \\ IEEE Cybersecurity Development Conference\\ Boston, MA\\ September 24th 2017
\item \textit{Building Hardened Internet-of-Things Clients using Language-Theoretic Security}\\ 4th LangSec Workshop at IEEE Symposium on Security and Privacy (Oakland)\\ San Jose, CA\\ May 25th 2017
\item \textit{Building vertically hardened Industrial-Control-Systems applications using Language-theoretic security}\\ 2nd CREDC Industrial Workshop\\ Tempe, AZ\\ March 28th 2017
\item \textit{Scalability Identity in the Internet of Things}\\ IEEE International Conference on Internet of Things\\ Chengdu, China\\ December 18th 2016
\end{itemize}

%\begin{comment}
%INSTRUCTION & Advising
%PUBS
\section*{Publications}


%% %SUBMITTED
%% \subsection*{Preprints}
%% \begin{itemize}
%% \end{itemize}

%PRINT/PRESS
\subsection*{Conferences and Workshops} %don't edit below line on H-index, use script instead

\begin{etaremune}
  \setlength\itemsep{0ex}

\item {\bf Prashant Anantharaman}, Kartik Palani, Rafael Brantley, Galen Brown, Sergey Bratus, Sean W. Smith\\
"PhasorSec: Protocol Security Filters for Wide Area Measurement Systems"\\
IEEE International Conference on Communications, Control, and Computing Technologies for Smart Grids, Aalborg, Denmark\\
October 29-31, 2018

	\item {\bf Prashant Anantharaman}, J. Peter Brady, Patrick Flathers, Vijay H. Kothari, Michael C. Millian, William G. Nisen, Jason Reeves, Nathan Reitinger, Sean W. Smith.\\
	"Going Dark: A Retrospective on the North American Blackout of 2038"\\
	New Security Paradigms Workshop (NSPW '18), Windsor, UK\\
	August 28-31, 2018

  \item Ioannis Agadakos*, Chien-Ying Chen*, Matteo Campanelli*, {\bf Prashant Anantharaman*}, Monowar Hasan*, Bogdan Copos*, Tancrede Lepoint, Michael Locasto, Gabriela F. Ciocarlie, Ulf Lindqvist \\
  		\textit{* Equal Contributions}\\
		"Jumping the Air Gap: Modeling Cyber-Physical Attack Paths in the Internet-of-Things" \\
		 3rd ACM CCS Cyber-Physical Systems Security and Privacy Workshop \\
		 November 2017
  \item {\bf Prashant Anantharaman}, Michael M. Millian, Sergey Bratus, Meredith L. Patterson.\\
  		"Input Handling Done Right: Building Hardened Parsers using Language-theoretic Security"\\
		 2nd IEEE Cybersecurity Development Conference, Boston, MA\\
		 September 2017
  
    \item {\bf P. Anantharaman}, M. Locasto, G. Ciocarlie, U. Lindqvist.\\
        "Building hardened Internet-of-Things implementations using Language-theoretic Security"\\
        IEEE Symposium on Security and Privacy -- Language-theoretic Security Workshop.\\
        May 2017
\item {\bf P. Anantharaman}, K. Palani, D. Nicol, S.W. Smith.\\
    "I am Joe's Fridge: Scalable Identity in the Internet of Things"\\
    IEEE International Conference on Internet of Things.\\
    December 2016
\item G. Ramakrishnan, {\bf P. Anantharaman}, and S. Mukherjee.\\
    "Proactive Resource Provisioning Model for Cloud Federation."\\
    International Conference on Distributed Computing and Internet Technology.\\
    January 2016
\end{etaremune}

%% \subsection*{Posters}

%% \begin{etaremune}
%% \setlength\itemsep{0ex}
%% \item \textbf{P. Anantharaman}, J. P. Brady, S. Bratus, I. R. Jenkins, M. Millian, D.M. Nicol, K. Palani, E. Reed, S.W. Smith\\
%%     "Increasing Cyber-Resilience of Large-Scale and Long-Lived Energy Delivery Infrastructure (EDI)"\\
%%     2nd CREDC Industry Workshop ,Tempe, AZ\\
%%     March 2017

%% \item \textbf{P. Anantharaman}, D.M. Nicol, K. Palani, E. Reed, S. W. Smith\\
%%     "Scalable Identity in the Smart Grid"\\
%%     2nd CREDC Industry Workshop ,Tempe, AZ\\
%%     March 2017
%% \item  K. Palani, {\bf P. Anantharaman}, D.M. Nicol, S. W. Smith\\
%%     "Namespace and Cryptographic Complexities in the Smart Grid"\\
%%     1st CREDC Industry Workshop ,Champaign, IL\\
%%     March 2016
%% \end{etaremune}

\section*{Teaching Experience}
\begin{itemize}
\setlength\itemsep{0ex}
\item Teaching Assistant for \textit{Programming Languages (COSC 59)}, September 2016-- November 2016.
		\subitem Fall 2016 (1 lecture). Instructor -- Dr. Sergey Bratus.
\item \textit{Ruby on Rails} Instructor at FSFTN Summer Camp, June 2015.
    \subitem Number of Participants: 120.
    \subitem Venue: IIT Madras.
\end{itemize}



\section*{Projects}
\subsection*{Hackathon Projects (Available on GitHub)}
\begin{itemize}
\setlength\itemsep{0ex}
  \item \textit{FoodRoach:} Locating the nearest location on campus providing free-food at a particular point of time. Software(s) used: \textsl{Ruby on Rails, Android}. \\ {\bf Winner - Best Dartmouth Hack.}
\item \textit{File Sharing Portal:} Developed a "Social Network for sharing of Files and Videos". Software(s) used: \textsl{Ruby on Rails, mysql}.
\item \textit{Guindy Times Website:} Developed the website and API for the college news magazine. \url{http://guindytimes.com}. Software(s) used: \textsl{Ruby on Rails, postgresql, Redis}
\item \textit{Kurukshetra : College Tech Fest Website:} Developed the website of the college tech fest. Developed the website and the API for the android application. \url{http://archive15.kurukshetra.org.in}. Software(s) used: \textsl{Ruby on Rails, mysql, angularjs}
\end{itemize}


\subsection*{Research Projects}

\begin{itemize}
\setlength\itemsep{0ex}

\item \textit{DARPA RADICS:} Building hardened parsers and setpoint monitoring capabilities for industrial control systems.

\item \textit{KeggyFuzzer:} Building smart fuzzers from parser-combinator input. We build a top-down fuzzer generator.

\item \textit{Tamil OCR and Error Correction:} This project was funded by "Centre for Technology Development and Transfer, Anna University". Error corrections were made on an OCRed document. We achieved an accuracy of almost 90\%. Software(s) used: \textsl{Java,Ruby on Rails, Tesseract OCR}

\end{itemize}


\subsection*{Academic Projects}
\begin{itemize}
  \setlength\itemsep{0ex}
  \item \textit{Kabali:} A ruby gem to inspect the YARV structures. Ruby YARV structures and stacks aren't so easy to inspect and comprehend, this gem would give you a step by step description of the modifications in the stack. {\bf Received a citation for this project.}
  \item \textit{Sankalan:} A ruby gem to make mdb and dtrace interchangeably.
  \item \textit{Yalnix:} A simple operating system in C. Implemented memory management and all syscalls as a part of the Operating Systems course.

  \end{itemize}


\section*{Programing Environments}
\setlength\itemsep{0ex}
\begin {itemize}
\setlength\itemsep{0ex}
\item Languages: C++, C, Java, Python, Ruby, HTML/CSS
\item Plaforms: Unix (Linux, Solaris)
\item Tools: Wireshark, Git version control, Emacs and vim text editors
\item Databases: Mysql, Postgresql, Oracle
\item Frameworks: Ruby on Rails, Django, LLVM, Hammer parser-combinator
\item Github account: https://github.com/prashantbarca
\end{itemize}

%AWARDS
\section*{Selected Fellowships and Awards}
\setlength\itemsep{0ex}
\begin {itemize}
\setlength\itemsep{0ex}
\item 50\% fee scholarship for first year of masters at Dartmouth College. 
\item TCS Award for Best Senior Thesis -- 2015
\end{itemize}

\end{document}
